Dotted Suffix Trees\\A Structure for Approximate Text Indexing

### 2005-08-12 paper/main.tex
Back in Europe
Small fixes. Longer, more detailed explanations.
Spell check
fix references

\documentclass[letter,10pt]{article}
\usepackage[boxruled,vlined,portugues,figure,linesnumbered,longend]{algorithm2e}
\input{figures/transfig}
\usepackage[]{graphicx}
\usepackage{QED}
\usepackage{amssymb}

\newcommand*{\Assign}{\ensuremath\longleftarrow}
\newcommand{\putstring}[1]{\textsl{#1}}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}

@@

\section{Introduction}
\input{introduction}

\section{The Indexing Structure}
\input{structure}
\section{Space Considerations}
\input{space}
\section{Searching}
\input{search}
\section{Constructing the Dotted Tree}
\input{construction}
\section{Experimental Results}
\input{experimental}
\section{Future Work, Open Problems}

In the example for the string \putstring{mississipi}, presented in Figure~\ref{fig:mississipi-1}, one can see that the tree below \putstring{s.i} and \putstring{ssi} are exactly the same. Whether such occurences are the basis for a significant space saving and what algorithms mightexploit them is an open question.
Along the same lines, the structure's definition might be extended to structures such as the suffix-DAG presented in~\cite[7.7]{gusfield:algorithms}. An algorithm to efficiently construct it over these suffix-DAGs is another open problem.

>>>>

\documentclass[a4paper,10pt]{article}
\usepackage[boxruled,vlined,portugues,figure,linesnumbered,longend]{algorithm2e}
\input{figures/transfig}
\usepackage[]{graphicx}
\usepackage{amssymb}
\usepackage{QED}

\newcommand*{\Assign}{\ensuremath\longleftarrow}
\newcommand{\putstring}[1]{\textsl{#1}}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\graphicspath{{figures/}}

@@

\section{Introduction}\label{sec:introduction}
\input{introduction}

\section{The Indexing Structure}\label{sec:structure}
\input{structure}

\section{Space Considerations}\label{sec:space}
\input{space}

\section{Searching}\label{sec:search}
\input{search}

\section{Constructing the Dotted Tree}\label{sec:construction}
\input{construction}

\section{Experimental Results}\label{sec:experimental}
\input{experimental}

\section{Future Work, Open Problems}\label{sec:future}

In the example for the string \putstring{mississipi}, presented in Figure~\ref{fig:mississipi-1}, one can see that the tree below \putstring{s.i} and \putstring{ssi} are exactly the same. Whether such occurrences are the basis for a significant space saving and what algorithms might exploit them is an open question.
Along the same lines, the structure's definition might be extended to structures such as the suffix-DAG presented in~\cite[7.7]{gusfield:algorithms}. An algorithm to efficiently construct it over these suffix-DAGs is another open problem.
